Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-11 paper.tex
Add a few explanatory bits

We may use Eqns.~\ref{eqn:ae_emissivity_feq} and \ref{eqn:se_emissivity}
to separate the source function thus
$\mathscr{S}=\mathscr{S}_{\rm AE}+\mathscr{S}_{\rm SE}$, with
\begin{align}
  \label{eqn:source_ae}
  \mathscr{S}_{\rm AE}
  &= \frac{\mathscr{K}_{\rm AE}}{\mathscr{K}} f^{\rm eq}, \\
  \label{eqn:source_se}
  \mathscr{S}_{\rm SE}
  &= \frac{\mathscr{K}_{\rm SE}}{\mathscr{K}} \Phi.
\end{align}
With these definitions we write a separated form of
Eqn.~\ref{eqn:boltzmann_linear_s}:
\begin{equation}
  \label{eqn:boltzmann_split}
  \frac{d}{d\lambda}f =
  \mathscr{K}_{\rm AE}(f^{\rm eq}-f)
  + \mathscr{K}_{\rm SE}(\Phi-f)
\end{equation}
From Eqn.~\ref{eqn:boltzmann_split} we see that
absorption/emission interactions drive the distribution function
toward $f^{\rm eq}$ over an affine lengthscale $\mathscr{K}_{\rm AE}^{-1}$,
and elastic scattering interactions drive it
toward $\Phi$ over an affine lengthscale $\mathscr{K}_{\rm SE}^{-1}$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-moving_fluid_avg_eps}
  \caption{Average energy $\langle\varepsilon\rangle=J/G$
    of neutrino fields for fluid moving in the $+z$ direction,
    with $A$ the angle between the neutrino momentum and the $+z$ direction.
    Test described in Sec.~\ref{ssec:test_doppler}.
    The points are computed from ray tracing spectra; the lines are the
    analytic formula.
  }
  \label{fig:avg_eps_doppler}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-collapse_profile_avg_eps_vs_cosA}
  \caption{Average energies in the collapse profile test,
    Sec.~\ref{ssec:test_collapse}.
    The observer is at 500~km, and the shock at 150~km,
    so that the half-opening angle of the shock is $\cos A=0.954$.
    The four methods depicted are 1) a fiducial Monte Carlo calculation,
    ray tracing using the 2) spectral and 3) gray methods to estimate background
    fields for scattering, and 4) ray tracing neglecting scattering.
  }
  \label{fig:avg_eps_collapse}
\end{figure}

>>>>

We may use Eqns.~\ref{eqn:ae_emissivity_feq} and \ref{eqn:se_emissivity}
to separate the source function thus
$\mathscr{S}=\mathscr{S}_{\rm AE}+\mathscr{S}_{\rm SE}$, with
\begin{align}
  \label{eqn:source_ae}
  \mathscr{S}_{\rm AE}
  &= \frac{\mathscr{K}_{\rm AE}}{\mathscr{K}} f^{\rm eq}, \\
  \label{eqn:source_se}
  \mathscr{S}_{\rm SE}
  &= \frac{\mathscr{K}_{\rm SE}}{\mathscr{K}} \Phi.
\end{align}
With these definitions we write a separated form of
Eqn.~\ref{eqn:boltzmann_linear_s}:
\begin{equation}
  \label{eqn:boltzmann_split}
  \frac{d}{d\lambda}f =
  \mathscr{K}_{\rm AE}(f^{\rm eq}-f)
  + \mathscr{K}_{\rm SE}(\Phi-f)
\end{equation}
From Eqn.~\ref{eqn:boltzmann_split} we see that
absorption/emission interactions drive the distribution function
toward $f^{\rm eq}$ over an affine lengthscale $\mathscr{K}_{\rm AE}^{-1}$,
and elastic scattering interactions drive it
toward $\Phi$ over an affine lengthscale $\mathscr{K}_{\rm SE}^{-1}$.
(Eqn.~\ref{eqn:proper_length} translates affine length to proper length
for a given observer; in this case the proper length scale is
$\varepsilon/\mathscr{K}$.)

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-moving_fluid_avg_eps}
  \caption{Average energy $\langle\varepsilon\rangle(\cos A)=J(\cos A)/G(\cos A)$
    of $\bar{\nu}_e$ neutrino fields for fluid moving in the $+z$ direction,
    with $A$ the angle between the neutrino momentum and the $+z$ direction.
    Test described in Sec.~\ref{ssec:test_doppler}.
    The points are computed from ray tracing spectra; the lines are the
    analytic formula.
  }
  \label{fig:avg_eps_doppler}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-collapse_profile_avg_eps_vs_cosA}
  \caption{Average energies $\langle\varepsilon\rangle(\cos A)=J(\cos A)/G(\cos A)$
    in the collapse profile test described in Sec.~\ref{ssec:test_collapse}.
    The observer is at 500~km, and the shock at 150~km,
    so that the half-opening angle of the shock is $\cos A=0.954$.
    The four methods depicted are 1) a fiducial Monte Carlo calculation,
    ray tracing using the 2) spectral and 3) gray methods to estimate background
    fields for scattering, and 4) ray tracing neglecting scattering.
  }
  \label{fig:avg_eps_collapse}
\end{figure}
